~\\[1in] % hack to put space at top.
\textbf{\Huge Acknowledgments}\\

\noindent 
First, I would like to thank my advisor, Prof. Angelo Cacciuto, for giving me the honor of being his first graduate student and being a never-ending source of ideas and knowledge.
Angelo always encouraged me to work hard and tackle interesting problems with his enthusiasm and support; working with him has been a pleasure, and I honestly can't imagine a better mentor. 
I hope that this dissertation will effectively convey the exciting work we did together.

I am also grateful to my defense committee: Prof. Bruce Berne and Prof. David Reichman, who have served on my graduate committee for the past five years and provided insightful feedback on my second-year defense and original research proposal, and, along with Prof. Luis Campos and Prof. Sanat Kumar, have taken the time out of their incredibly busy schedules to read my dissertation and attend my defense.

Scientific research is a collaborative effort, and I have benefited from exceptional collaboration with other members of the Cacciuto group.
In particular, I had the privilege of working extensively with Dr. Behnaz Bozorgui Katherine Klymko, Dr. Josep P\`{a}mies, and Maya Sen.
I would also like to thank Leo PeBenito and Clarion Tung, with whom my collaboration has been less direct but no less valuable, and especially An{\dj}ela \v{S}ari\'{c} -- for large parts of the past four years, the two of us have \textit{been} the Cacciuto group. 

I would like to thank my many friends here at Columbia.
They made graduate school much more enjoyable, and I wish them all the best as they transition from school to the real world.

\newpage
I want to express my sincere gratitude to my family.
They have always been my strongest supporters, and have always been there for me unconditionally; my academic success would not have been possible without the encouragement my parents have given me since I was a child.

Finally, of course, I am thankful to Christine Vanos.
Graduate school isn't easy, but she made it much easier, and I'm looking forward to spending the rest of my life with her.

%\hspace{0.7\textwidth}{\today} \\
\hspace{0.7\textwidth}William L. Miller
